The error when inferring phylogenies with incipient species by a Birth-Death model

### 2018-04-10 article.tex
Fix bug

From a species tree, we simulate a DNA alignment that has the same history
as the phylogeny. The nucleotides of the DNA alignment follow a JC69
nucleotide substitution model, in which all nucleotide-to-nucleotide transitions
are equally likely. Although this may seem as a simplification, in our Bayesian
inference (see below) we can use this exact site model as a prior, which we 
know is the truth.
The DNA sequence length and mutation rate was chosen as such to provide one
nucleotide change per 1000 years per lineage. As our time unit is in 
millions of years, this equates to a rate of 1000 nucleotide substitutions 
changes per time unit per lineage. To provide for each substitution being unique,
we simulate as much DNA nucleotides as expected mutations, which equals the
nucleotide substitution rate times the crown age, which equals 15K. As this
mutation rate is constant over all branches, it in effect follows a strict 
clock model, which we will specify as the known clock model prior later.

>>>>

From a species tree, we simulate a DNA alignment that has the same history
as the phylogeny. The nucleotides of the DNA alignment follow a JC69
nucleotide substitution model, in which all nucleotide-to-nucleotide transitions
are equally likely. Although this may seem as a simplification, in our Bayesian
inference (see below) we can use this exact site model as a prior, which we 
know is the truth.
The DNA sequence length and mutation rate was chosen as such to provide one
nucleotide change per 1000 years per lineage. As our time unit is in 
millions of years, and our crown age is 15 million years,
this equates to a rate of $\frac{1000}{15}$ nucleotide substitutions 
changes per time unit per lineage. To provide for each substitution being unique,
we simulate as much DNA nucleotides as expected mutations, which equals the
nucleotide substitution rate times the crown age, which equals 15K. As this
mutation rate is constant over all branches, it in effect follows a strict 
clock model, which we will specify as the known clock model prior later.
